\bf Calendar-based graphics for visualizing people's daily schedules

### 2018-10-23 main.Rmd
manuscript ready

However, the conventional displays of time series data obscure patterns relative to special events (such as public holidays and recurring cultural/sport events), which may appear fascinating to viewers.

@@

```{r time-series-plot, fig.height = 6, fig.cap = "Time series plots showing the number of pedestrians in 2016 measured at three different sensors in the city of Melbourne. Colored by the sensors, small multiples of lines show that the foot traffic varies from one sensor to another in terms of both time and number. A spike occurred at the State Library, caused by the annual White Night event on 20th of February. A relatively persistent pattern repeats from one week to another at Flagstaff Station. Birrarung Marr looks rather noisy and spiky, with chunks of missing records."}
```

```{r facet-time, fig.height = 6, fig.cap = "Hourly pedestrian counts for 2016 faceted by sensors and days of the week using lines. It primarily features two types of seasons---time of day and day of week---across all the sensors. Apparently other factors have influence over the number of pedestrians, which cannot captured by the faceted plots, such as the overnight White Night traffic on Saturday at the State Library and a variety of events at Birrarung Marr."}
```

@@

Plots can be layered. The comparison of sensors can be done by overlaying plot the values for each (Figure \ref{fig:overlay}). Differences between the pedestrian patterns at these sensors can be seen. Flagstaff Station exhibits strong commuters patterns, with fewer pedestrian counts during the weekends and public holidays. This suggests that Flagstaff Station has limited functionality on non-work days. From Figure \ref{fig:overlay} it can be seen that Birrarung Marr has a distinct temporal trend from the other two all year around. The nighttime events, such as White Night and New Year's Eve, have barely affected the operation of Flagstaff Station but heavily affected the incoming and outgoing traffic to the State Library and Birrarung Marr.

@@

To avoid the overlapping problem, the calendar layout can be embedded into a series of subplots for the different sensors. Figure \ref{fig:facet} presents the idea of faceting calendar plots. This allows comparing the overall structure between sensors, while emphasizing individual sensor variation. In particular, we can immediately learn that when Birrarung Marr was crowded and why, such as Australian Open in the last two weeks of January. This does not pop out in the conventional graphics.

>>>>

However, the conventional displays of time series data conceal patterns relative to special events (such as public holidays and recurring cultural/sport events), which may be worth noting to viewers.

@@

```{r time-series-plot, fig.height = 6, fig.cap = "Time series plots showing the number of pedestrians in 2016 measured at three different sensors in the city of Melbourne. Colored by the sensors, small multiples of lines show that the foot traffic varies from one sensor to another in terms of both time and number. A spike occurred at the State Library, caused by the annual White Night event on 20th of February. A relatively persistent pattern repeats from one week to another at Flagstaff Station. Birrarung Marr looks rather noisy and spiky, with a couple of chunks of missing records."}
```

```{r facet-time, fig.height = 6, fig.cap = "Hourly pedestrian counts for 2016 faceted by sensors and days of the week using lines. It primarily features two types of seasons---time of day and day of week---across all the sensors. Apparently other factors have influence over the number of pedestrians, which cannot be captured by the faceted plots, such as the overnight White Night traffic on Saturday at the State Library and a variety of events at Birrarung Marr."}
```

@@

Plots can be layered. The comparison of sensors can be done by overlaying plot the values for each (Figure \ref{fig:overlay}). Differences between the pedestrian patterns at these sensors can be seen. Flagstaff Station exhibits strong commuters patterns, with fewer pedestrian counts during the weekends and public holidays. This suggests that Flagstaff Station has limited functionality on non-work days. From Figure \ref{fig:overlay} it can be seen that Birrarung Marr has a distinct temporal trend from the other two all year round. The nighttime events, such as White Night, have barely affected the operation of Flagstaff Station but heavily affected the incoming and outgoing traffic to the State Library and Birrarung Marr.

@@

To avoid the overlapping problem, the calendar layout can be embedded into a series of subplots for the different sensors. Figure \ref{fig:facet} presents the idea of faceting calendar plots. This allows comparing the overall structure between sensors, while emphasizing individual sensor variation. In particular, it can be immediately learned that when Birrarung Marr was busy and packed, for example Australian Open in the last two weeks of January. This is concealed in the conventional graphics.

### 2018-10-23 main.tex
manuscript ready

\caption{Time series plots showing the number of pedestrians in 2016 measured at three different sensors in the city of Melbourne. Colored by the sensors, small multiples of lines show that the foot traffic varies from one sensor to another in terms of both time and number. A spike occurred at the State Library, caused by the annual White Night event on 20th of February. A relatively persistent pattern repeats from one week to another at Flagstaff Station. Birrarung Marr looks rather noisy and spiky, with chunks of missing records.}\label{fig:time-series-plot}
\end{figure}

@@

\caption{Hourly pedestrian counts for 2016 faceted by sensors and days of the week using lines. It primarily features two types of seasons---time of day and day of week---across all the sensors. Apparently other factors have influence over the number of pedestrians, which cannot captured by the faceted plots, such as the overnight White Night traffic on Saturday at the State Library and a variety of events at Birrarung Marr.}\label{fig:facet-time}
\end{figure}

>>>>

\caption{Time series plots showing the number of pedestrians in 2016 measured at three different sensors in the city of Melbourne. Colored by the sensors, small multiples of lines show that the foot traffic varies from one sensor to another in terms of both time and number. A spike occurred at the State Library, caused by the annual White Night event on 20th of February. A relatively persistent pattern repeats from one week to another at Flagstaff Station. Birrarung Marr looks rather noisy and spiky, with a couple of chunks of missing records.}\label{fig:time-series-plot}
\end{figure}

@@

\caption{Hourly pedestrian counts for 2016 faceted by sensors and days of the week using lines. It primarily features two types of seasons---time of day and day of week---across all the sensors. Apparently other factors have influence over the number of pedestrians, which cannot be captured by the faceted plots, such as the overnight White Night traffic on Saturday at the State Library and a variety of events at Birrarung Marr.}\label{fig:facet-time}
\end{figure}
